Random Forests, LAs

### 2024-01-27 src/la_RF.Rmd
for bham presentation

path.out <- paste0(path, "/outputs/rf/figures/test_regions.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()

>>>>

path.out <- paste0(path, "/outputs/rf/figures/test_regions_LA.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()
